\documentclass[../main.tex]{subfiles}
\graphicspath{{\subfix{./Resources/images/}}}

\begin{document}
% Main Body
\chapter{Taking Excellent Notes}

\begin{outline}[enumerate]

\1 Excellent notes use an \underline{Outline} format
	\2	\dracRed{This is required for my class to get your points for notes!}
	\2 This works in all of your classes.
\1 Examples
	\2 \dracGreen{Good}\\

	\marginnote{Note the good indentation $\mapsto$}


	1. Main Idea 1

	\quad a. Detail 1

	\quad b. Detail 2

	\marginnote{Indentation $\mapsto$ represents more specific stuff}

	\quad \quad i) Detail about Detail 2

	\quad \quad i) Another detail about Detail 2

	\quad c. Detail 3

	2. Main Idea 2

	etc...\\

	\2 \dracRed{Bad}\\

	\marginnote{Nothing is indented.  This is hard to read and find information later.  Indenting is an easy way to make your notes better.}

	1. Main Idea 1

	a. Detail 1

	b. Detail 2

	i) Detail about Detail 2

	i) Another detail about Detail 2

	c. Detail 3

	2. Main Idea 2

	etc...\\


	\1 It is better to over-indent than under-indent.

	\1 Style

		\2 Choose whatever style you like the most.  You can use any combination of the following:

	\begin{displayquote}

	1. Numbers

	\quad a. Letters

	\quad \quad i) Roman Numerals

	\quad \(\bullet\) Bullet Points

	\quad \quad $\Box$ Boxes

	\quad $\rotatebox[origin=c]{180}{$\Lsh$}$ Curly Arrows

	\quad \quad - Dashes
	\end{displayquote}


	\1 Other useful symbols and conventions
	\marginnote{Put misc. things you want to remember in the margins.}

	$\bullet$ \quad \textbf{Bolding}, \underline{Underlining} and \underline{\underline{Double Underlining}} your text to represent important words.

	$\bullet$ \quad $\Delta$ Greek letter "Delta".  In math and science, means "Change".

	$\bullet$ \quad $\Rightarrow$ Double arrows for definitions.

	$\bullet$ \quad $\leadsto$ Squiggly arrows for saying when one things leads to another thing.

	$\bullet$ \quad $\approx$ For when things are about the same.

	$\bullet$ \quad $\dashrightarrow$ Dashed arrows.

	$\bullet$ \quad $\bigstar$ For really important stuff that you want to call out.

	$\bullet$ \quad \fbox{Put a box around definitions.}

	$\bullet$ \quad \fbox{\fbox{Double Box formulas.}}

	\margincloud{Put questions or thoughts in the margins with clouds}

	\1 Advanced / Extra stuff

	\2 \dracPurple{To really take your notes to the next level, incorporate colors.}

	\2 \colorbox{dracCyan}{\dracRed{Bring different colored pens and highlighters to draw attention to specific details.}}

	\2 \dracOrange{Come up with your own system of what each color means.}

\end{outline}
\end{document}
